A Framework for Substructural Type Systems \thanks{Supported by organization x.}

### 2022-01-21 tex/esop22/syntax.tex
[ edit ] TODO list

Finally, a \AgdaRecord{System} consists of a set of rule labels (i.e.,
constructor names), and for each label a decsription of the
corresponding rule. We use $\rhd$ as infix notation for systems to
associate the label set with the rules.

>>>>

Finally, a \AgdaRecord{System} consists of a set of rule labels (i.e.,
constructor names), and for each label a description of the
corresponding rule. We use $\rhd$ as infix notation for systems to
associate the label set with the rules.
